Bootstrapping Multi-atlas Hippocampal Segmentation with MAGeT

### 2013-03-12 paper.Rnw
Added normals and normality tests to the ADNI1 Screening histogram as per Tris's comments

\begin{figure}[h]
<<ADNI-scr-histogram,dependson='ADNI-baseline-volumes-boxplot',cache=T>>=
melted = melt(complete_totals, measure.vars=c( "SNT","FSL","FS","MAPER","MAGeT"))
ggplot(data=melted, aes(x=value)) + 
       geom_histogram(binwidth=250) +
       facet_grid( variable ~ DX) 
@
  \caption{{\bf ADNI Baseline cohort.} Comparison of HC volumes by FreeSurfer
  (FSF), MAGeT brain (MAGeT), MAPER, and manual (SNT).}
  \label{ADNI-scr-histogram}
\end{figure}

>>>>

\begin{figure}[h]
<<ADNI-scr-histogram,dependson='ADNI-baseline-volumes-boxplot',cache=T>>=
melted   = melt(complete_totals, measure.vars=c( "SNT","FSL","FS","MAPER","MAGeT"))
binwidth = 250

# prepare the normals
grid <- with(melted, seq(min(value), max(value), length = 100))
normaldf <- ddply(melted, c("variable", "DX"), function(df) {
  data.frame( 
    value = grid,
    density = dnorm(grid, mean(df$value), sd(df$value)),
    freq = length(df$value) * dnorm(grid, mean(df$value), sd(df$value)) * binwidth,
    length = length(df$value)
  )
})

testsdf <- ddply(melted, c("variable", "DX"), function(df) {
  shapiro = shapiro.test(df$value)
  data.frame(
    shapiro.w = shapiro$statistic,
    shapiro.p = shapiro$p.value,
    mean = mean(df$value),
    sd = sd(df$value)
  )
})

label_x_pos = 10000
ggplot(data=melted, aes(x=value)) + 
  geom_histogram(binwidth=binwidth, alpha=0.8) + 
  geom_line(aes(y=freq, colour='red'), data=normaldf) +
  geom_text(aes(y=29,x=label_x_pos,hjust=1,size=1, 
                label=paste("list(W ==",signif(shapiro.w, digits=3), ", p == ", 
                            signif(shapiro.p,digits=3), ")")
                ), parse=TRUE,
            data=testsdf) + 
  geom_text(aes(y=25,x=label_x_pos,hjust=1,size=1, 
                label=paste("sigma ==",signif(sd, digits=3))), parse=TRUE,
            data=testsdf) + 
  geom_text(aes(y=21,x=label_x_pos,hjust=1,size=1, 
                label=paste("mu ==",signif(mean, digits=3))), parse=TRUE,
            data=testsdf) + 
  xlim(0, 10000) + ylim(0,30) + 
  facet_grid(variable ~ DX) + 
  scale_colour_discrete(legend=FALSE) + 
  scale_size_continuous(legend=FALSE) + 
  labs(title="Total hippocampus volume by disease and measurement method", 
       x=expression(paste("Total hippocampal volume (", mm^2, ")")),
       y="Frequency") + 
  opts(axis.title.x = theme_text(vjust=-0.1))
@
  \caption{{\bf ADNI Baseline cohort.} Comparison of total hippocampal volumes as measured by SNT, FSL, FreeSurfer (FS), MAPER, and MAGeT brain (MAGeT). A fitted normal curve is shown in red. $W$ is the Shapiro-Wilkes test statistic measuring normality of the data (low p-values indicate non-normality).}
  \label{ADNI-scr-histogram}
\end{figure}
